---
title: "World of Tanks Data by Region"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

## World of Tanks Different Regions

World of Tanks is a global game and thus runs on 4 major distinct servers. The US server encompasses the North American region, the EU server covers most of the EU region, the RU servers covers primarily Russia but also Eastern Europe, the SEA covers most of Eastern Asia. In general the EU, US, and RU servers are run fairly similar when it comes to new updates and tanks released. The SEA servers are run by a seperate company which has a degree of freedom when it comes to new content added. It is important to note that due to the ongoing conflict in Ukraine, Wargaming has effectively exited Russia and Belarus and handed control of the RU server to a Belorussian company so the status of the RU server may change in the near future.

## The World of Tanks Playerbase

When calculating the number of play, a "play" is added to the count whenever a player hits the "play" button in the lobby. Because there are usually 30 players in a game this means that a single game will typically add 30 counts to the "play" count (this is approximate as there are bots and games with less than 30 players meaning that there are many games with less than 30 players). As of now: 
```{r}
total <- tank_statsreg %>%
  summarise(`Total Plays` = sum(`Total played`))
print(paste("There are a total of", total, "plays in the past 60 days."))
```

