---
title: "Tank Win Rates Based on Varying Attributes"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rvest)
library(scales)
library(purrr)

wotscrapewr <- function(x,y){
  tableda <- x %>%
    read_html() %>%
    html_nodes("table#stat_veh_all4")  %>% 
    html_table() %>% 
    .[[1]] %>%
    setNames(c('Name','Tier','Type','Nation',paste('Total Played',y, sep=" "),paste('Wins',y, sep=" "), paste('Win %',y, sep=" "),paste('Unique Players',y, sep=" "), 'Region'))
}
wot_tableeu <- wotscrapewr("https://wot-news.com/stat/server/eu/norm/en/", "EU")
wot_tableus <- wotscrapewr("https://wot-news.com/stat/server/us/norm/en/", "US") 
wot_tableru <- wotscrapewr("https://wot-news.com/stat/server/ru/norm/en/", "RU") 
wot_tablesea <- wotscrapewr("https://wot-news.com/stat/server/sea/norm/en/", "SEA") 
other_info <- read_csv("~/STA 518/Final-Project/tank_stats.csv") %>%
  select("Name", "Premium")

wot_list <- list(wot_tableeu, wot_tableus, wot_tableru, wot_tablesea, other_info)
tank_statstot <- wot_list %>% reduce(inner_join, by="Name")

tank_statstot <- tank_statstot %>%
  select(-ends_with(".y"),-ends_with("x.x")) %>%
  rename("Tier"=`Tier.x`, "Nation"=`Nation.x`, "Type"=`Type.x`)


#Get Values for the total World of Tanks player base by adding up all the servers
tank_statstot <- tank_statstot %>%
  mutate("Total Played" = `Total Played US` + `Total Played EU` + `Total Played SEA` + `Total Played RU`, "Total Wins" = `Wins US` + `Wins EU` + `Wins SEA` + `Wins RU`, "Total Unique Players" = 
           `Unique Players US` + `Unique Players EU` + `Unique Players SEA` + `Unique Players RU`, "Win Rate %" = (`Total Wins`/`Total Played`)*100)

#Filter out Repeat Values and Low Observation Values (tanks in beta testing)
tank_statstot <- tank_statstot[!duplicated(tank_statstot$Name),] %>%
  filter(`Total Played` > 6000)

#Convert "Tier" and "Premium" into a character values and order them 
tank_statstot$`Tier` <- as.character(tank_statstot$`Tier`) %>%
  factor(levels=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))
tank_statstot$`Premium` <- as.character(tank_statstot$`Premium`)

#Rename Premium
tank_statstot <- tank_statstot%>%
  mutate(Type = fct_recode(Type,
                           "Medium Tank" = "Medium Tanks",
                           "Heavy Tank" = "Heavy Tanks",
                           "Light Tank" = "Light Tanks",
                           "Tank Destroyer" = "TD",
                           "Artillery" = "SPG")) %>%
  
  mutate(Nation = fct_recode(Nation,
                             "United States" = "Usa",
                             "USSR" = "Ussr",
                             "United Kingdom" = "UK")) %>%
  
  mutate(Premium = fct_recode(Premium,
                              "No" = "0",
                              "Yes" = "1"))

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

## The Tanks in World of Tanks

World of tanks contains more than 600 different tanks. All of them have different characteristics. This project will use a few characteristics such as Type, Tier, Nation, and its premium status to see if they have any major effect on winrate.

### Tank Type

World of Tanks separates their tanks into 5 different categories; light tanks, medium tanks, heavy tanks, tank destroyers, and artillery. In general, these tanks all fit into a different niche. Light tanks are the scouts for the team, running ahead to spot enemy tanks for their teamate to shoot at. Medium tanks are you're jack-of-all trades class, being decent in most aspects but not spectacular. Heavy utilize their heavy armor to take and hold the most important parts of the map. Tank destroyers sit behind using their powerful guns to snipe enemies from a distance. Artillery are the support class, specializing in removing dug in opponents from an extreme range. Looking at the data, are any of these niches appear to be more influential than others?

### Current Percentage Breakdown for Tank Type

```{r}
tank_statstot %>%
  group_by(Type) %>%
  summarise(`Type Played` = sum(`Total Played`)) %>%
  mutate(Percent = `Type Played` / sum(`Type Played`)) %>%
  mutate(labels = scales::percent(Percent)) %>%
  group_by(Type)%>%
  ggplot(aes(x = "", y = Percent, fill = Type)) +
  geom_col(color="black") +
  geom_text(aes(x=1.5, label = labels),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())
```

At the moment, the player base appears to be preferring playing heavy tanks, medium tanks, and tank destroyers the most. This does make sense considering light tanks are somewhat difficult to play and artillery is generally seen as boring to play by much of the player base.

### Boxplot of Tank Type by Win Rate
```{r}
tank_statstot %>%
  ggplot(mapping=aes(x=`Win Rate %`,group=Type, color=Type)) +
  geom_boxplot()
```

### Mean Win Rate by Tank Type
```{r}
tank_statstot %>%
  group_by(Type) %>%
  summarise("Mean Win Rate by Tank Type" = mean(`Win Rate %`), "Total Number of Type" = length(`Win Rate %`))
```

### ANOVA Test on Tank Type
```{r}
aov(`Win Rate %` ~ Type, data = tank_statstot) %>%
  summary()
```
Simply looking at the comparative boxplots and observing the mean win rate for each class, it appears fairly apparent that Wargaming has balanced their tank classes fairly well. Performing an ANOVA test on the variable Type give us a p-value well above any threshold we would use to conclude Type has any noticeable effect on win rate. 

## Tank Tier 

World of Tanks uses a matchmaker system to make for balanced teams every match. Based on this, they have a built in tier system with each tank attached to a certain tier based on how powerful that tank is. In this case, tier 1 includes the weakest tanks in the game while tier 10 includes the most powerful tanks. World of Tanks has a built in matchmaker that will make sure there are an equal number of tank from each tier on each team. Different tiers can be matched up with tank +/- 2 tier from their own. So for example, a tier 5 tank oculd be matched with tier 3, 4, 5, 6, and 7 tanks although there will always be an equal number of tier 5's on each team. Are there any differences between the winrates of different tiers? 

### Current Percentage Breakdown for Tank Tier

```{r}
tank_statstot %>%
  group_by(Tier) %>%
  summarise(`Tier Played` = sum(`Total Played`)) %>%
  mutate(Percent = `Tier Played` / sum(`Tier Played`)) %>%
  mutate(labels = scales::percent(Percent)) %>%
  group_by(Tier)%>%
  ggplot(aes(x = "", y = Percent, fill = Tier)) +
  geom_col(color="black") +
  geom_text(aes(x=1.5, label = labels),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())
```

It appears that about 2/3 games played are at tier 8, 9 and 10. This makes sense as they require the most work to get to and thus take the most time to get the XP needed to move up to the next tier. On top of this, many players enjoy playing at tier 10 because they are the most powerful they can get. Tier 8 makes sense because it is the tier of the most popular premium tanks, tier 8 also has the most tanks out of any tier in the game.

### Boxplot of Tank Tier by Win Rate
```{r}
tank_statstot %>%
  ggplot(mapping=aes(x=`Win Rate %`,group=Tier, color=Tier)) +
  geom_boxplot()
```

### Mean Win Rate by Tank Tier
```{r}
tank_statstot %>%
  group_by(Tier) %>%
  summarise("Mean Win Rate by Tank Tier" = mean(`Win Rate %`), "Total Number of Tier" = length(`Win Rate %`))
```

### ANOVA Test on Tank Tier
```{r}
aov(`Win Rate %` ~ Tier, data = tank_statstot) %>%
  summary()
```

Looking at the boxplot, the different tiers appear to be fairly even in winrate with the exception of tier 1 which is significantly lower overall. Tier 8 also appears somewhat smaller but less so than tier 1. It is important to note that the tiers with the 2 lowest winrates have the most and least amount of tanks in those tier respectably. The mean winrate for each tier also indicates a similar trend. Performing an ANOVA test on the variable Type give us a p-value that does appear to indicate that tier does seem to have a statistically significant effect on a tanks win rate.

## Tank Nationality 

World of Tanks includes a variety of different tanks from different nations. Each nation tends to have a somewhat different play style but they are suppose to be generally balanced with all nations said to be just as powerful as the others. There are certainly claims that some nations are more powerful than others. Particularly, that Russian tanks are overall better due to a large portion of the player base being from Russia. There are also claims that because German tanks were some of the first tanks released in the game, they are generally not as powerful as the newer tanks. However, does the data support any of these claims.

### Current Percentage Breakdown for Tank Nationality

```{r}
tank_statstot %>%
  group_by(Nation) %>%
  summarise(`Nation Played` = sum(`Total Played`)) %>%
  mutate(Percent = `Nation Played` / sum(`Nation Played`)) %>%
  mutate(labels = scales::percent(Percent)) %>%
  group_by(Nation)%>%
  ggplot(aes(x = "", y = Percent, fill = Nation)) +
  geom_col(color="black") +
  geom_text(aes(x=1.5, label = labels),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())
```

It appears that the majority of games played are from the US, USSR/Russia, Germany or France. This does make sense for two reasons. To start, these nations have the most tanks in the game so they have more options in general for people to choose and players will naturally spend more time playing nations with more tanks. Second, these nations all have a server that can claim a nation as their own. The US server has US tanks, RU server has USSR/Russian tanks and so on. 

### Boxplot of Tank Nation by Win Rate
```{r}
tank_statstot %>%
  ggplot(mapping=aes(x=`Win Rate %`,group=Nation, color=Nation)) +
  geom_boxplot()
```

### Mean Win Rate by Tank Nation
```{r}
tank_statstot %>%
  group_by(Nation) %>%
  summarise("Mean Win Rate by Tank Nation" = mean(`Win Rate %`), "Total Number of Nation" = length(`Win Rate %`))
```

### ANOVA Test on Tank Nation
```{r}
aov(`Win Rate %` ~ Nation, data = tank_statstot) %>%
  summary()
```

Looking at the boxplots, the different nations appear to be fairly even in winrate with the exception of Swedish tanks and Japanese tanks which are noticeably lower overall. It also appears that Germany has the 3 best tanks in the game according to win rate. The means appear to support these observations as well. Performing an ANOVA test on the variable Type give us a p-value that appears to indicate that a tanks nation doesn't seem to have a statistically significant effect on a tanks win rate. This means that while Sweden and Japan do appear to have some differences, they aren't enough to be seen a statistically significant. Interestingly enough, it appears that while players say Russian tanks are overly powerful, the opposite appears to be true with Russian tanks mean win rate being the 3rd lowest out of all the nations. While at the same time, German tanks tend to have a relatively high mean win rate overall.

## Premium Tanks 

Finally, one way that Wargaming works to monetize their game is to sell unique tanks for real world currency. These tanks are wholly unique just like all other tanks and many times support very unique or niche play styles. However, over the years, there have been claims that Wargaming intentionally makes these tanks more powerful than the normal tanks in order to incentivize their purchases. These claims of being "pay-to-win" have been prevalent for a long time. However, does the data appear to support these claims.

### Current Percentage Breakdown for Premium Tank Games Played

```{r}
tank_statstot %>%
  group_by(Premium) %>%
  summarise(`Premium Played` = sum(`Total Played`)) %>%
  mutate(Percent = `Premium Played` / sum(`Premium Played`)) %>%
  mutate(labels = scales::percent(Percent)) %>%
  group_by(Premium)%>%
  ggplot(aes(x = "", y = Percent, fill = Premium)) +
  geom_col(color="black") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())
```

The data shows that almost 1/3 of all games played are played with a premium tank. This is actually rather high and indicates that a large portion of the game is now played with tanks that cost real world currency. This could be due to a gameplay advantage or players might want to make sure they were getting their moneys worth out of purchasing a tank. 

### Boxplot of Premium Status by Win Rate
```{r}
tank_statstot %>%
  ggplot(mapping=aes(x=`Win Rate %`,group=Premium, color=Premium)) +
  geom_boxplot()
```

### Mean Win Rate by Premium Status
```{r}
tank_statstot %>%
  group_by(Premium) %>%
  summarise("Mean Win Rate by Premium Status" = mean(`Win Rate %`), "Total Number of Premium/Non-Premiums" = length(`Win Rate %`))
```

### ANOVA Test on Premium Status
```{r}
aov(`Win Rate %` ~ Premium, data = tank_statstot) %>%
  summary()
```

Looking at the boxplots, there does appear to be a significant difference in the win rate between premium and non-premium tanks. Looking at the means, premium tanks appear to have an almost 2% high winrate than non-premium tanks. Running an ANOVA test on the premium status of the tanks, the p-value is very low indicating that premium status does certainly seem to effect the win rate of a tank.